---
title: "Math 493 Homework 1"
output: html_notebook
---

### Creating Vectors and Matrices

```{r}
# Assign to the symbol A the 3-by-5 matrix with entries 0.
A = matrix(0,3,5)
# Assign value 1 to the 2nd row, 4th column element of A
A[2,4] = 1
#Assign value 2 to all entries of 5th column of A
A[,5]=2
```

### Set Operations

A finite set is a distinct object from a vector in that the elements are assumed to be distinct and the order of the elements in immaterial. 

```{r}
# Given two sequences: 
a = c(1, 2, 3, 4, 3, 0, 0, 5, -1)
b = c(4, 3, 2, 7, 7, 0, 1)

# Let the respective sets of elements be
A = unique(a)
B = unique(b)

# The intersection of A and B is
intersect(a,b)
# The union of the two sets is
union(a, b)
# The set of elements of A not in B is given by 
setdiff(a, b)
```


### Simple Programming
Computer programs require conditional statements and loops. A few examples are given
here. It is most convenient to write your program as a separate text that you can edit before running. R has its
own script editor. You may run your finished script simply by pasting the text to the R command line window.
(You can also run the script from the editor window by highlighting the part of the script you wish to run and
then clicking on the button ‘run’ at the top of the window.)
Monte Carlo simulations typically involve repeating a random experiment many times. The ‘for loop’ is particularly
useful in this case as you can see in the following experiment: We generate 10000 2-by-2 matrices with
random elements in the range [−1, 1] (with the uniform probability distribution.) We then wish to find the mean
value of the determinant.

```{r}
# number of random matrices
n = 1000
# keep track of the sum of determinant
# at each step of the for loop
total = 0
for (i in 1:n) {
  # the main part of the experiment to be repeated is here:
  matrix_elements = runif(4, min=-1, max=1)
  # assemble the matrix using these four random numbers:
  random_matrix = matrix(matrix_elements, nrow=2, byrow=TRUE)
  # add the matrix's determinant to total
  total = total + det(random_matrix)
}
meanVal = total/n
```

```{r}
N=50000
numbers=c(1:50) 
count = 0
for (i in 1:N){
  a = sample(numbers,5,replace=FALSE) 
  if(is.element(1,a) || is.element(2,a) ){
    count = count + 1
  }
}
output = count / N

```

